On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-10-04 paper.tex
Rewriting stuff

\begin{prop}[\text{\cite[Proposition 3.10]{LS17}}] \label{prop:rel-presentation}
 Assume that $I$ is a splitting ideal of a commutative ring $R$. 
 Then for any $\ell\geq 3$ the group $\St(\rA_\ell,\,R,\,I)$ can be presented by means of two families of generators $F(u,\,v)$, $S(v,\,u)$
  (where $u\in \E(n,\,R)e_1,$ and $v\in I^n$ are such that $u^tv=0$) subject to the following relations:
\begin{align}
&F(u,\,v)F(u,\,w)=F(u,\,v+w), \label{add4}\\
&S(u,\,v)S(w,\,v)=S(u+w,\,v), \label{add5}\\
&F(u,\,v)F(u',\,v')F(u,\,v)^{-1}=F(t(u,\,v)u',\,t(v,\,u)^{-1} v'), \label{conj3} \\
&F(ge_1,\,g^*e_2a)=S(ge_1a,\,g^*e_2),\ \text{for all}\ a\in I,\, g \in E(n, R). \label{coef-move}
\end{align}
\end{prop}
\begin{rem}
Although we will not need this, using essentially the same reasoning as in~\cite[Proposition~8]{S15} it is not hard to show that 
$\St(\rA_\ell, R, I)$ still admits the above presentation without the assumption that $I$ is splitting.
\end{rem}

@@

To simplify notation, throughout this section we set $N_1 = N(\varpi_1)$, $N^1 = N(-\varpi_1)$.
We only construct one of the desired maps from the definition of $\sigma$-pair, namely $\sigma(\varpi_1^\vee) \colon N_1 \to N^1$,
 for shortness we denote it by $\sigma_1$.

@@

It is easy to define the first map $(\sigma_1)_{P_1^-(A)}$, indeed, using the decomposition $P_1^-(A) \cong U^-_1 \rtimes L_1$ where 
\[U^-_1 = \langle x_{i1}(\xi) \mid i\neq 1,\ \xi\in A \rangle \text{ and } L_1 = \langle x_{ij}(\xi) \mid i,  j \neq 1,\ \xi\in A\rangle \]
we apply the universal property of semidirect products once again 
and define $(\sigma_1)_{P_1^-(A)}$ by requiring that it acts identically on $L_1$ (notice that $L_1 \subseteq N^1$) %TODO: Language???
and acts on elements of $U^-_1$ via the formula $(\sigma_1)_{P_1^-(A)}(x_{i1}(\xi))= x_{i1}(t\xi)$.

To define the map $(\sigma_1)_{N_{1,0}}$ we invoke the presentation of the relative Steinberg group $\St(n, A[t], tA[t])$ given in~\cref{prop:rel-presentation}.
%and the elements constructed in~\cref{sec:another-presentation}. in the special case $R=A[t]$, $I=tA[t]$.
%We only verify the second assertion for $F(u, v)$  and only in the special case $g = x_{hk}(\xi) \in \mathcal{X}^1$, $g' = t_{hk}(\xi') \in \pi(\mathcal{X}_1)$.

Denote by $\delta_1$ the matrix $d_1(t) \in \GL(A[t, t^{-1}])$ from~\cref{exm:chi-linear}.
Now for $u \in E(n, A[t])$ and $v \in tA[t]$ we can define the map $\sigma_1$ on the generators of $N_{0}=\St(n, A[t], tA[t])$ 
 using the elements defined in~\cref{sec:another-presentation}:
\begin{equation*}
 (\sigma_1)_{N_0} (F(u, v)) = X_{\delta_1 \cdot t^{-1}}(u, v),\ (\sigma_1)_{N_0} (S(v, u)) = Y_{\delta_1}(v, u).
\end{equation*}

\begin{comment}
\begin{equation}
 \sigma_1(F(u, v)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot t u, \delta_1 \cdot t^{-1} v_i),\ \
 \sigma_1(S(v, u)) = \prod\limits_{i=1}^r x(\delta_1^{-1} \cdot v_i, \delta_1 \cdot u).
\end{equation}

\begin{lemma} \label{lem:cor-conj}
 \begin{lemlist}
   \item \label{item:correctness} The elements $\sigma_1(F(u, v))$ and $\sigma_1(S(v, u))$ are well-defined, i.\,e. they do not depend on the choice of decomposition for $v$.
   \item \label{item:conjugation} For any $g \in N^1$ one has 
      \begin{equation}
          \nonumber {}^g\left(\sigma_1(F(u, v))\right) = \sigma_1\left(F(g' \cdot u, {g'}^{*} \cdot v)\right),\ \ 
                    {}^g\left(\sigma_1(S(u, v))\right) = \sigma_1\left(S(g' \cdot u, {g'}^{*} \cdot v)\right),                    
      \end{equation}
      where $g' = {}^{\delta_1}\pi(g).$
 \end{lemlist}
\end{lemma}
\end{comment}

\begin{prop}
 If $A$ is a local ring them the map $(\sigma_1)_{N_0}$ preserves relations~\eqref{add4}--\eqref{coef-move}.
 In particular, the map $(\sigma_1)_{N_0}$ is well-defined.
\end{prop}
\begin{proof}
 For~\eqref{add4}--\eqref{add5} this is an immediate corollary of~\cref{item:xsmall-additivity} and~\cref{lem:xy-wd}
 For~\eqref{conj3} this follows from the second part of the lemma applied in the special case $g = \sigma_1(F(u, v)) \in N^1$.
\end{proof}

It remains to verify that $\sigma_1$ preserves~\eqref{coinc}.
Let us do this at first in the special case when $g^*$ belongs to the subset $G_0 = H_{12}(R) \cdot U^+_1(R) \cdot U^-_1(R)$.
Here we denote by $H_{12}(R)$ the subgroup of $T(n, R)$ generated by semisimple root elements $ h_{12}(\xi)$, $\xi \in R^*$.

Since the only nonzero components of $u = g^* \cdot e_2$ are $u_1$ and $u_2$ we can present $v = g \cdot e_1$ as a sum $v' + v''$, where 
 $v'_i=0$, $i>2$ and $v''_1=v''_2=0$.
Since $v', v'' \in D(u)$ and $u \in D(v)$, from the definition of $\sigma_1$ we obtain that:
\begin{multline} \label{eq:special-case}
 \sigma_1(S(g \cdot e_1a, g^* \cdot e_2)) = x(\delta_1^{-1} \cdot v'a, \delta_1\cdot  u) \cdot x(\delta_1^{-1}\cdot v''a, \delta_1 \cdot u) = \\
  = x(\delta_1^{-1} va, \delta_1 \cdot u) = x(\delta_1^{-1} vat^{-1}, \delta_1 \cdot ut) = \sigma_1(F(g \cdot e_1, g^* \cdot e_2a)) 
\end{multline}

To obtain the assertion in the general case notice that for $R$ local the group $\E(n, R)$ admits the following decomposition:
\[\E(n, R) = \mathrm{EP}_1(R) \cdot H_{12}(R) \cdot U^-_1(R) \cdot U^+_1(R).\]
This can be either obtained as a corollary of Gauss decomposition or can be proved by a direct calculation. %TODO: Give reference

Applying transpose-inverse automorphism $(-)^*$ to the above decomposition and invoking~\cref{lem:n1-decomp} we obtain that $\E(n, R[t]) = \pi(N_1) \cdot G_0$.
Thus, every $g \in \E(n, R[t])$ can be factored as $\pi(n) \cdot h$ for some $n\in N_1$ and $h \in G_0$.
Since $\pi(n) = {}^{\delta_1} \pi(n')$ for some $n' \in N^1$ it remains to apply~\cref{item:conjugation} and~\eqref{eq:special-case} to obtain the required assertion:
\begin{multline} \nonumber \sigma_1(F(g \cdot e_1, g^* \cdot e_2a)) = {}^{n'}(\sigma_1(F(h \cdot e_1, h^* \cdot e_2a))) = \\
                           = {}^{n'}(\sigma_1(S(h \cdot e_1a, h^* \cdot e_2))) = \sigma_1(S(g \cdot e_1a, g^* \cdot e_2)). \end{multline}

>>>>

\begin{prop}[\text{\cite[Proposition 3.10]{LS17}}] \label{prop:rel-presentation}
 Assume that $I$ is a splitting ideal of a commutative ring $R$. 
 Then for any $\ell\geq 3$ the group $\St(\rA_\ell,\,R,\,I)$ can be presented by means of two families of generators $F(u,\,v)$, $S(v,\,u)$
  (where $u\in \E(n,\,R)e_1,$ and $v\in I^n$ are such that $u^tv=0$) subject to the following relations:
\begin{align}
&F(u,\,v)F(u,\,w)=F(u,\,v+w), \label{add4}\\
&S(u,\,v)S(w,\,v)=S(u+w,\,v), \label{add5}\\
&F(u,\,v)F(u',\,v')F(u,\,v)^{-1}=F(t(u,\,v)u',\,t(v,\,u)^{-1} v'), \label{conj3} \\
&F(me_1,\,m^*e_2a)=S(me_1a,\,m^*e_2),\ \text{for all}\ a\in I,\, m \in \E(n, R). \label{coef-move}
\end{align}
\end{prop}
\begin{rem}
Although we will not need this, using essentially the same reasoning as in~\cite[Proposition~8]{S15} it is not hard to show that 
$\St(\rA_\ell, R, I)$ still admits the above presentation without the assumption that $I$ is splitting.
\end{rem}

@@

To simplify notation, throughout this section we set $N_1 = N(\varpi_1^\vee)$, $N^1 = N(-\varpi_1^\vee)$.
We only construct one of the desired maps from the definition of $\sigma$-pair, namely $\sigma(\varpi_1^\vee) \colon N_1 \to N^1$,
 for shortness we denote it by $\sigma_1$.

@@

It is easy to define the first map $(\sigma_1)_{P_1^-(A)}$, indeed, using the decomposition $P_1^-(A) \cong U^-_1 \rtimes L_1$ where %TODO: Language???
\[U^-_1 = \langle x_{i1}(\xi) \mid i\neq 1,\ \xi\in A \rangle \text{ and } L_1 = \langle x_{ij}(\xi) \mid i,  j \neq 1,\ \xi\in A\rangle \]
we apply the universal property of semidirect products once again 
and define $(\sigma_1)_{P_1^-(A)}$ by requiring that it acts identically on $L_1$ (notice that $L_1 \subseteq N^1$) %TODO: Language???
and acts on elements of $U^-_1$ via the formula $(\sigma_1)_{P_1^-(A)}(x_{i1}(\xi))= x_{i1}(t\xi)$.

%To define the map $(\sigma_1)_{N_{0}}$ we invoke the presentation of the relative Steinberg group $\St(n, A[t], tA[t])$ given in~\cref{prop:rel-presentation}.

Denote by $\delta_1$ the matrix $d_1(t) \in \GL(A[t, t^{-1}])$ from~\cref{exm:chi-linear}.
Now for $u \in \E(n, A[t])$ and $v \in (tA[t])^n$ we can define the map $(\sigma_1)_{N_0}$ on the generators of $N_{0}=\St(n, A[t], tA[t])$ 
 using the elements defined in~\cref{sec:another-presentation}:
\begin{equation*}
 (\sigma_1)_{N_0} (F(u, v)) = X_{\delta_1 \cdot t^{-1}}(u, v),\ (\sigma_1)_{N_0} (S(v, u)) = Y_{\delta_1}(v, u).
\end{equation*}
It is clear that the above elements belong to $N^1$.

\begin{prop}
 If $A$ is a local ring them the map $(\sigma_1)_{N_0}$ preserves relations~\eqref{add4}--\eqref{coef-move}.
 In particular, the map $(\sigma_1)_{N_0}$ is well-defined.
\end{prop} 
\begin{proof}
 For~\eqref{add4}--\eqref{add5} this is an immediate corollary of~\cref{item:xsmall-additivity} and~\cref{lem:xy-wd}.
 By~\cref{lem:xy-conj} for $g \in N^1$ one has 
 \begin{equation} \label{eq:xy-conj-n1}
  g \cdot X_{\delta_1 t^{-1}}(u', v') \cdot g^{-1} = X_{\delta_1 t^{-1}}(mu', m^*v'), \text{ where } m = \delta_1 \cdot \phi(g) \cdot \delta_1^{-1}.
 \end{equation}
 To obtain that $(\sigma_1)_{N_0}$ preserves~\eqref{conj3} it remains to put $g = X_{\delta_1 t^{-1}}(u, v)$.

 Let us verify that $\sigma_1$ preserves~\eqref{coef-move}, i.\,e. that for $a\in tA[t]$ and $m \in \E(n, A[t])$ one has
 $X_{\delta_1 t^{-1}}(me_1, m^*e_2 a) = Y_{\delta_1}(me_1 a, m^* e_2)$.
 Let us do this at first in the special case when $m^* \in \E(n, A[t])$ belongs to the subset $G_0 = H_{12}(A) \cdot U^+_1(A) \cdot U^-_1(A)$.
 Here we denote by $H_{12}(A)$ the subgroup of $T(n, A)$ generated by semisimple root elements $ h_{12}(\xi)$, $\xi \in A^*$.

 Since the only nonzero entries of $v = m^* e_2$ are $v_1$ and $v_2$ we can write $u = m e_1$ as a sum $u' + u''$, where 
  $u'_i=0$, $i>2$ and $u''_1=v''_2=0$.
 Since $u', u'' \in D(u)$ and $u \in D(v)$, from Lemmas~\ref{lem:xy-wd}--\ref{lem:xy-conj} we obtain that:
 \begin{multline} \label{eq:special-case}
  Y_{\delta_1}(me_1 a, m^* e_2) = x(\delta_1^{-1} \cdot u'a, \delta_1\cdot  v) \cdot x(\delta_1^{-1}\cdot u''a, \delta_1 \cdot v) = \\
   = x(\delta_1^{-1} ua, \delta_1 \cdot v) = x(\delta_1^{-1}t \cdot u, \delta_1t^{-1} \cdot v a) = X_{\delta_1 t^{-1}}(me_1, m^*e_2 a).
\end{multline}

 To obtain the assertion in the general case notice that for $A$ local the group $\E(n, A)$ admits the following decomposition:
 \[\E(n, A) = \mathrm{EP}_1(A) \cdot H_{12}(A) \cdot U^-_1(A) \cdot U^+_1(A).\]
 This can be either obtained as a corollary of Gauss decomposition or can be proved by a direct calculation. %TODO: Give reference

 Applying transpose-inverse automorphism $(-)^*$ to the above decomposition and invoking~\cref{lem:n1-decomp} we obtain that $\E(n, A[t]) = \phi(N_1) \cdot G_0$.
 Thus, every $m \in \E(n, A[t])$ can be factored as $\phi(n) \cdot h$ for some $n\in N_1$ and $h \in G_0$.
 Since $\phi(n) = \delta_1 \phi(n') \delta_1^{-1}$ for some $n' \in N^1$ it remains to apply~\eqref{eq:xy-conj-n1} and~\eqref{eq:special-case}: 
 \begin{multline} \nonumber X_{\delta_1 t^{-1}}(me_1, m^*e_2 a) = {}^{n'}(X_{\delta_1 t^{-1}}(he_1, h^*e_2 a)) = \\
                            = {}^{n'}(Y_{\delta_1}(he_1 a, h^*e_2)) = Y_{\delta_1}(me_1 a, m^* e_2). \end{multline} 
\end{proof}
